---
title: "Household Wealth Inequality in a Synthetic Sample"
subtitle: "A compact gallery document for testing publication-inspired styles"
author:
  - name: "Ada Template"
    dept: "Department of Sociology"
    inst: "Queens College, City University of New York"
    email: "ada.template@example.edu"
date: "`r format(Sys.Date(), '%B %d, %Y')`"

institution: "Research Design Gallery"
series: "Style Test"
surname: "Template"
runningtitle: "Style Gallery"

abstract: |
  This short document tests title treatment, headings, ordinary prose,
  tables, figures, code, mathematical notation, and closing matter across
  each document type and visual style.

keywords:
  - scholarly design
  - R Markdown
  - research communication

acknowledgements: |
  This synthetic acknowledgement is included to check title-page spacing and
  secondary metadata.

fontpath: "../inst/fonts/"
numbersections: true
doublespace: false
linenumbers: false
maincolumns: 1

output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = FALSE,
  fig.width = 5.5,
  fig.height = 3.2
)
```

# Introduction

This gallery document is deliberately ordinary. It includes a short empirical
argument, a table, a chart, inline code such as `median_wealth`, and a small
amount of mathematical notation. The goal is to reveal whether a style can
handle common research material without requiring the author to redesign the
document by hand.

## Data and Measures

The example uses a synthetic table of household wealth by educational
attainment. A production document would describe the sample, weights,
measurement period, and missing-data rules in more detail.

```{r table-example}
summary_table <- data.frame(
  group = c("No degree", "BA", "Graduate"),
  median_wealth = c(42000, 180000, 325000),
  share = c(0.52, 0.31, 0.17)
)
knitr::kable(summary_table, caption = "Synthetic household wealth by education")
```

## Model Sketch

Inline math should sit comfortably in the line, as in
$y_i = \alpha + \beta x_i + \epsilon_i$.

$$
\bar{x} = \frac{1}{n}\sum_{i=1}^{n} x_i
$$

# Findings

The main pattern is intentionally simple: median wealth rises with educational
attainment. The figure is not meant to be analytically interesting; it is a
stress test for caption placement, plot sizing, and the relationship between
figures and body text.

```{r figure-example}
barplot(
  summary_table$median_wealth,
  names.arg = summary_table$group,
  col = c("#D9E2EC", "#8FB3D9", "#2E6FA3"),
  border = NA,
  ylab = "Median wealth",
  las = 1,
  cex.axis = 0.75,
  cex.lab = 0.85,
  cex.names = 0.8
)
```

# Implications

Different audiences need different visual signals. A journal reviewer may want
conventional restraint, a policy reader may need clear signposting, and a
public audience may need a stronger editorial entry point. The package styles
are designed to let the author choose that communication setting directly.

# References

No bibliography is required for this synthetic gallery document.

