---
title: "Fontset Test: default"
subtitle: "Synthetic document for visual regression checks"
date: "May 2026"

author:
  - name: "Ada Template"
  - name: "Sam Sample"

surname: "Template"
runningtitle: "Fontset Test: default"

author_dept: "Department of Sociology"
author_inst: "Queens College, City University of New York"
author_addr: "65-30 Kissena Blvd., Queens, NY 11367, USA"
author_email: "ada.template@example.edu"
author_web: "https://example.edu/fontset-test"
author_orcid: "0000-0002-1825-0097"

institution: "Household Finance Working Group"
series: "Fontset Test Series"
number: 1

bibliography: "fontset-test.bib"
csl: "../inst/csl/default.csl"

anonymize: false
doublespace: false
linenumbers: false
numbersections: true
maincolumns: 1

abstract: |
  This fake manuscript tests title-page metadata, body typography,
  citations, headings, mathematical notation, tables, figures, and code
  formatting across the available docdesigner template fontsets.

keywords:
  - font testing
  - R Markdown
  - LaTeX template

acknowledgements: |
  This synthetic acknowledgement is included to test the title-page
  acknowledgement block and its spacing.

output:
  pdf_document:
    template: "../inst/templates/docdesignertemplate.tex"
    latex_engine: pdflatex
    keep_tex: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE, fig.width = 5, fig.height = 3)
```

# Introduction

This paragraph exercises ordinary prose, *emphasis*, **strong emphasis**,
inline code such as `median_income`, and citations [@burnham2002; @warren2015].
The metadata citation should also resolve cleanly [@docdesigner2026].

## Mathematical Notation

Inline math should sit comfortably in text, as in $y_i = \alpha + \beta x_i + \epsilon_i$.

$$
\bar{x} = \frac{1}{n}\sum_{i=1}^{n} x_i
$$

## Table and Code

```{r table-example}
summary_table <- data.frame(
  group = c("No degree", "BA", "Graduate"),
  median_wealth = c(42000, 180000, 325000),
  share = c(0.52, 0.31, 0.17)
)
knitr::kable(summary_table, caption = "Synthetic household wealth by education")
```

## Figure

```{r figure-example}
barplot(
  summary_table$median_wealth,
  names.arg = summary_table$group,
  col = c("#D9E2EC", "#8FB3D9", "#2E6FA3"),
  border = NA,
  ylab = "Median wealth",
  las = 1,
  cex.axis = 0.75,
  cex.lab = 0.85,
  cex.names = 0.8
)
```

# Conclusion

The final section gives section headings, spacing, references, and running
headers a little more room to show themselves.
