---
title: "Style Gallery Slides"
subtitle: "A compact ioslides test deck"
author: "Ada Template"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

## Research Question

How does a style system change the feel of the same research material?

## Key Finding

Median wealth rises sharply across the synthetic education groups.

```{r, echo=FALSE}
summary_table <- data.frame(
  group = c("No degree", "BA", "Graduate"),
  median_wealth = c(42000, 180000, 325000)
)
barplot(
  summary_table$median_wealth,
  names.arg = summary_table$group,
  col = c("#D9E2EC", "#8FB3D9", "#2E6FA3"),
  border = NA,
  ylab = "Median wealth",
  las = 1
)
```

## Methods Note

```{r}
model <- lm(median_wealth ~ seq_along(group), data = summary_table)
coef(model)
```

## Implication

The same empirical content can read as a working paper, policy brief, public
essay, scientific communication, or technical presentation depending on the
chosen style.

